\documentclass[UTF8,a4paper,10pt]{article}

% \begin{equation*}
%   \begin{aligned}
%   \end{aligned}
% \end{equation*}

% \begin{mybox}{}
% \end{mybox}


% \begin{Problem}[]{}
% \end{Problem}

% \begin{solution}\,
% \end{solution}
  

% \begin{enumerate}[label=(\alph*)]
% \end{enumerate} 

% \setcounter{section}{3} 
% \setcounter{theorem}{3}

% \begin{theorem}\label{thm:3.4}
%   If $E = \bigsqcup_{k} E_k$ is a countable union of sets, then $|E|_e \leq \sum_{k} |E_k|_e$.
%   \end{theorem}

%  \footcite[][42]{Wheeden_Zygmund_2015}

\input{preamble.tex}

\begin{document}



\begin{Problem}[]{}
 Let $f : \mathbb{R} \rightarrow \mathbb{C}$. Prove that $f$ satisfies the Lipschitz condition
  \[
  |f(x) - f(y)| \leq M|x - y|
  \]
  for some $M > 0$ and for all $x, y \in \mathbb{R}$, if and only if $f$ satisfies the following two properties:
  \begin{enumerate}
      \item[(i)] $f$ is absolutely continuous.
      \item[(ii)] $|f'(x)| \leq M$ for a.e. $x$
  \end{enumerate}
  
\end{Problem}

\(\Rightarrow \)

Suppose \(f\) is Lipschitz continuous. For \(\epsilon > 0\), let \(\delta = \frac{\epsilon}{M}\), whenever \( \sum |b_i - a_i|< \delta\), we have

\[\sum |f(b_i) - f(a_i)| \leq M \sum |b_i - a_i| < \epsilon,\]

implying that \(f\) is absolutely continuous.

By Theorem 7.27 and Corollary 7.23, we can see that \(f'\) exists (\(f\) is differentiable) almost everywhere.

For \(x\) where \(f'(x)\) exists, the Lipschitz condition implies that, for all \(h\),

\begin{equation*}
  \begin{aligned}
    \left| \frac{f(x+h) - f(x)}{h} \right| \leq M
  \end{aligned}
\end{equation*}

Taking the limit as \(h\to 0\), we have

\begin{equation*}
  \begin{aligned}
    \left|f'(x) \right|  = \lim_{h\to 0}\left| \frac{f(x+h) - f(x)}{h} \right| \leq M
  \end{aligned}
\end{equation*}

\dotfill

\(\Leftarrow \)

Suppose that \(f\) is absolutely continuous. By Theorem 7.27 and Corollary 7.23, we have that \(f\) is of bounded variation and thus \(f'\) exists almost everywhere.

By Theorem 7.29, for all \(x < y \in \mathbb{R} \),

\[\left| f(x) - f(y) \right| = \left| \int_{x}^{y} f'(t) \, dt \right| \leq \int_{x}^{y} \left| f'(t) \right| \, dt \leq \int_{x}^{y}  M \, dt = M \left| x - y \right|.
\]

We can conclude that \( f \) is Lipschitz continuous.

\begin{mybox}{Corollary 7.23}
  If \( f \) is of bounded variation on \([a, b]\), then \( f' \) exists almost everywhere in \([a, b]\), and \( f' \in L[a, b] \).
\end{mybox}

\begin{mybox}{Theorem 7.27}

  If \( f \) is absolutely continuous on \([a, b]\), then it is of bounded variation on \([a, b]\).

\end{mybox}


\begin{mybox}{Theorem 7.29}

A function \( f \) is absolutely continuous on \([a, b]\) if and only if \( f' \) exists almost everywhere in \([a, b]\), \( f' \) is integrable on \([a, b]\), and for \( a \leq x \leq b \),
\[
f(x) - f(a) = \int_{a}^{x} f'(t) \, dt.
\]
\end{mybox}

\pagebreak

\begin{mybox}{}
    
  A function \( \phi \) is convex in \( (a, b) \) if and only if
  \[
    \phi(\theta x_1 + (1 - \theta) x_2) \leq \theta \phi(x_1) + (1 - \theta) \phi(x_2)
    \]
    for \( x_1 , x_2 \in (a,b)\) and \( 0 \leq \theta \leq 1 \). 
    
  \end{mybox}

  \begin{mybox}{Theorem 7.40}


 If \(\phi\) is convex in (a, b), then \(\phi\) is continuous in (a, b). Moreover,
\(\phi\) exists except at most in a countable set and is monotone increasing.

\end{mybox}

\begin{Problem}[]{}
  Prove that $f$ is convex on $(a, b)$ if and only if it is continuous and
  \[
  f\left(\frac{x + y}{2}\right) \leq \frac{f(x) + f(y)}{2}
  \]
  for all $x, y \in (a, b)$.
  

\end{Problem}

\(\Rightarrow \)

Suppose that \(f\) is convex. Following the definition of convexity, let \(\theta = \frac{1}{2}\), we have

\[
  f\left(\frac{x + y}{2}\right) \leq \frac{f(x) + f(y)}{2}
  \]
  for all $x, y \in (a, b)$.
  
By Theorem 7.40, \(f\) is continuous.

\dotfill

\(\Leftarrow \)

% Suppose that \(f\) is continuous and the inequality holds.

% Let a sequenence \(d_k = \frac{m}{2^n}\), where \(n \in\mathbb{N}\), and \(m = 0,1,\ldots,2^n\).

% For all \(d_k\), we have 

% \[
%   f\left(d_k a + (1-d_k) b\right) 
%    \leq d_k f(a) + (1-d_k) f(b)
%   \]

% For any \(\theta \in [0,1]\), we can find \(\lim_{k\to \infty}d_k = \theta\).





% \dotfill

Suppose that \( f \) is continuous and satisfies the midpoint inequality for all \( x, y \in (a, b) \).

To prove convexity, consider any \( x, y \in (a, b) \) and any \( \theta \in [0, 1] \). We need to show that
\[
f(\theta x + (1-\theta) y) \leq \theta f(x) + (1-\theta) f(y).
\]

This can be proved using an induction approach on the dyadic rationals (i.e., numbers of the form \( \frac{m}{2^n} \), where \(n \in\mathbb{N}\), and \(m = 0,1,\ldots,2^n\)), then generalizing to all \( \theta \) using the continuity of \( f \).

\textit{Base Case:} For \( n=1 \), the midpoint inequality ensures that the convexity condition holds for \( \theta = \frac{1}{2} \).

% \textit{Inductive Step:} Assume the convexity condition holds for all dyadic rationals of the form \( \frac{m}{2^n} \) for some \( n \). Consider \( \theta = \frac{m}{2^{n+1}} \) or \( \theta = 1 - \frac{m}{2^{n+1}} \). Through a detailed calculation using the inductive hypothesis, this can be shown to satisfy the convexity condition.

\textit{Inductive Step:} Assume the condition holds for \( n \). Consider \( \theta = \frac{m}{2^{n+1}} \).

\textit{Case 1:} If \( m \) is even, \( \theta \) is a dyadic rational of the form \( \frac{k}{2^n} \), so the hypothesis applies.

\textit{Case 2:} If \( m \) is odd, write \( \theta \) as
\[
\theta = \frac{1}{2} \left(\frac{(m-1)/2}{2^n}\right) + \frac{1}{2} \left(\frac{(m+1)/2}{2^n}\right),
\]
noting that \(\frac{m-1}{2}\) and \(\frac{m+1}{2}\) are integers.
% both terms being dyadic rationals of order \( n \).

Using the midpoint inequality:
\[
f\left(\theta x + (1-\theta) y\right) \leq \frac{1}{2} f\left(\frac{(m-1)/2}{2^n} x + \left(1 - \frac{(m-1)/2}{2^n}\right) y\right) + \frac{1}{2} f\left(\frac{(m+1)/2}{2^n} x + \left(1 - \frac{(m+1)/2}{2^n}\right) y\right).
\]
By applying the convexity condition assumed for \( \frac{(m-1)/2}{2^n} \) and \( \frac{(m+1)/2}{2^n} \):
\begin{equation*}
  \begin{aligned}
f\left(\theta x + (1-\theta) y\right) &\leq \frac{1}{2} \left(\frac{(m-1)/2}{2^n} f(x) + \left(1 - \frac{(m-1)/2}{2^n}\right) f(y)\right) + \frac{1}{2} \left(\frac{(m+1)/2}{2^n} f(x) + \left(1 - \frac{(m+1)/2}{2^n}\right) f(y)\right) \\
&= \theta f(x) + (1-\theta) f(y).
\end{aligned}
\end{equation*}

Thus, the convexity condition is preserved for \( n+1 \).


The continuity of \( f \) implies that since the inequality holds for all dyadic rationals, it also holds by the limit for any \( \theta \in [0, 1] \) as dyadic rationals are dense in \([0,1]\).

Thus, \( f \) is convex on \((a, b)\).


\end{document}